ACNP 2024 MS ANXIETY

### 2024-09-11 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_FINAL_20240911.Rmd
final, with figs, verifying T with promis

2. Demographics (age, sex, race, +/- PHQ2, PHQ9, has anxiety dx, on anxiety meds, both, on dmt) -> elena to make all the csvs into tables
3. PROMIS scores (each type of measure is a line, y axis is score, x axis is anxiety dose)
4. Some sort of schematic of pipeline (Maggie) - 
  a. amygdala - mpfc blobs
  b. uncinate connecting the two
  c. white matter lesion dropped in uncinates
  d. streamline filtering
  e. mean of both side
5. Mean UF Anxiety diagnosis either violin or bar
6. Mean Anxiety dose either violin or bar

7. Supplement: 
 - More detailed streamline filtering
 - Depression group uncinate burden
 - Fornix diagnosis and dose; depression group 
 - Corr mean_UF with social problems?

## Make final data frame for analysis
### read in emr data
```{r read_in_df}
homedir <- "/Users/eballer/BBL/msanxiety/"

@@

# dose 2, "(T = 2.88, df = 6, P = 0.028, Cohen's d =  -0.69, Effect size = medium)"
physical_vs_mental_health_anxiety_severeA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "T")
print(physical_vs_mental_health_anxiety_severeA[1])

@@

physical_vs_mental_health_anxiety_mildA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], paired = "T")
print(physical_vs_mental_health_anxiety_mildA[1])

@@

physical_vs_mental_health_anxiety_noA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], paired = "T")
print(physical_vs_mental_health_anxiety_noA[1])

@@

physical_health_noAvsSevereA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "F")
print(physical_health_noAvsSevereA[1])

###mental health, sick vs healthy - (T = 3.68, df = 8.13, P = 0.006, Cohen's d =  -1.87, Effect size = large)
mental_health_noAvsSevereA <- t_and_cohen_d(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
print(mental_health_noAvsSevereA[1])

#construct df of p values
p_and_cohen_values <- t(data.frame(rbind(c(physical_vs_mental_health_anxiety_noA[2],
                         physical_vs_mental_health_anxiety_mildA[2],
                         physical_vs_mental_health_anxiety_severeA[2],
                         mental_health_noAvsSevereA[2],
                         physical_health_noAvsSevereA[2]),
                         c(physical_vs_mental_health_anxiety_noA[3],
                         physical_vs_mental_health_anxiety_mildA[3],
                         physical_vs_mental_health_anxiety_severeA[3],
                         mental_health_noAvsSevereA[3],
                         physical_health_noAvsSevereA[3])), 
                         row.names = c("p", "cohen_d")))

@@

rownames(p_and_cohen_values) <- t_test_names

#fdr correct
p_and_cohen_values <- as.data.frame(p_and_cohen_values) %>%
  mutate(fdr = round(p.adjust(p, method = "fdr"),3)) %>%
  mutate(p = as.numeric(p)) %>%
  mutate(cohen_d = as.numeric(cohen_d)) %>%
  relocate(cohen_d, .after = fdr)

print(p_and_cohen_values)

#write output, will be used in supplement
write.csv(p_and_cohen_values, file = paste0(homedir, "/results/promis_pairwise_p_and_cohen_d_values.csv"), row.names = TRUE)

#save ones that meet correction
pfdr_0.05 <- p_and_cohen_values %>%
  filter(fdr <0.05)

>>>>

2. Demographics (age, sex, race, +/- PHQ2, PHQ9, has anxiety dx, on anxiety meds, both, on dmt) -> elena to make all the csvs into tables
3. PROMIS scores (each type of measure is a line, y axis is score, x axis is anxiety dose)
4. Some sort of schematic of pipeline (Maggie) - 
  a. amygdala - mpfc blobs
  b. uncinate connecting the two
  c. white matter lesion dropped in uncinates
  d. streamline filtering
  e. mean of both side
5. Mean Anxiety dose either violin or bar

6. Supplement: 
 - Promis tables
#Rstduio Version: 2024.04.1+748 (2024.04.1+748)
## Make final data frame for analysis
### read in emr data
```{r read_in_df}
homedir <- "/Users/eballer/BBL/msanxiety/"

@@

# dose 2, "(T = 2.88, df = 6, P = 0.028, Cohen's d =  -0.69, Effect size = medium)"
physical_vs_mental_health_anxiety_severeA <- t_p_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "T")
print(physical_vs_mental_health_anxiety_severeA[1])

@@

physical_vs_mental_health_anxiety_mildA <- t_p_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], paired = "T")
print(physical_vs_mental_health_anxiety_mildA[1])

@@

physical_vs_mental_health_anxiety_noA <- t_p_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], paired = "T")
print(physical_vs_mental_health_anxiety_noA[1])

@@

physical_health_noAvsSevereA <- t_p_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "F")
print(physical_health_noAvsSevereA[1])

###mental health, sick vs healthy - (T = 3.68, df = 8.13, P = 0.006, Cohen's d =  -1.87, Effect size = large)
mental_health_noAvsSevereA <- t_p_and_cohen_d(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired="F")
print(mental_health_noAvsSevereA[1])

#construct df of p values
t_p_and_cohen_values <- t(data.frame(rbind(c(physical_vs_mental_health_anxiety_noA[2],
                         physical_vs_mental_health_anxiety_mildA[2],
                         physical_vs_mental_health_anxiety_severeA[2],
                         mental_health_noAvsSevereA[2],
                         physical_health_noAvsSevereA[2]),
                         c(physical_vs_mental_health_anxiety_noA[3],
                         physical_vs_mental_health_anxiety_mildA[3],
                         physical_vs_mental_health_anxiety_severeA[3],
                         mental_health_noAvsSevereA[3],
                         physical_health_noAvsSevereA[3]),
                         c(physical_vs_mental_health_anxiety_noA[4],
                         physical_vs_mental_health_anxiety_mildA[4],
                         physical_vs_mental_health_anxiety_severeA[4],
                         mental_health_noAvsSevereA[4],
                         physical_health_noAvsSevereA[4])), 
                         row.names = c("t", "p", "cohen_d")))

@@

rownames(t_p_and_cohen_values) <- t_test_names

#fdr correct
t_p_and_cohen_values <- as.data.frame(t_p_and_cohen_values) %>%
  mutate(t = as.numeric(t)) %>%
  mutate(fdr = round(p.adjust(p, method = "fdr"),3)) %>%
  mutate(p = as.numeric(p)) %>%
  mutate(cohen_d = as.numeric(cohen_d)) %>%
  relocate(cohen_d, .after = fdr)

print(t_p_and_cohen_values)

#write output, will be used in supplement
write.csv(t_p_and_cohen_values, file = paste0(homedir, "/results/promis_pairwise_t_p_and_cohen_d_values.csv"), row.names = TRUE)

#save ones that meet correction
pfdr_0.05 <- t_p_and_cohen_values %>%
  filter(fdr <0.05)
